Buildtime Trend

### 2016-01-28 buildtimetrend/btt_fosdem2016.tex
move dashboard screenshot forward, improve text
move who's using it, change 'free for open source' slide

    Collection of Bash and Python scripts, generating, analysing and visualising timing data:

@@

    Service :

@@

      \item get Travis CI build logfile

@@

      \item visualise using a dashboard with trends

@@

          \item parse buildlog

@@

    \pause

@@

    \frametitle{Business model}

@@

      \item offering the service costs money

@@

	  \item hosting the service
          \item storing the data
      \item Github inspired business model : free for Open Source, paying for private repos
      \item Further development with real data gathering : better feedback

>>>>

    A script to generate a chart with duration of build stages :

@@

    Webservice is triggered at the end of a build :

@@

      \item download Travis CI build logfile

@@

      \item visualise using a dashboard with charts

@@

          \item buildlog parser

@@

@@

    \frametitle{Who can use it}

@@

      \item Webservice : Free for Open Source (for now)

@@

      \item pyca/cryptography
      \item Pootle
